---
title: "Package Development Workshop notes"
author: "Allison R. Mason"
date: "2023-09-18"
output: pdf_document
---

What libraries do we have?
```{r}
.libPaths()
```

I have one, but common to have 2.

Packages with compiled code are usually stored as binary and has code (fortran, c, etc) that is not compiled - this means you need to compile that code locally and you may not have all the machinery to do this so R will ask if you want to install a prior verson from source and use this instead.

Recommend turning off restore .RData for package development, so you have a new workspace to play with the package

```{r, include=FALSE}
usethis::use_devtools() # this will silently autoload devtools on R startup

# packages for package development:
  library(devtools)
  library(roxygen2)
  library(testthat)
  library(knitr)
  library(pkgdown) # for package website
```

# Create package with devtools
```{r}
# create_package("~/Desktop/libminer")
# commented out, as this only needs to be run once
```

# Initiate a git repository for the packaage
```{r}
# git vaccinate will help with protecting you from yourselff by adding global .gitignore

# git_sitrep() # this will show you your gobal git status/setup

# use_git() # commented out, as this only needs to be run once
```

# Create the first function
```{r}
use_r("lib-summary")
```

The use_r() will create a new .R file in the /R with the name specified.

# now how to get the functions into memory from the source
```{r}
load_all()
```

The load_all() will take the source code and load all the functions into R memory.


